---
title: "Exploring incontinence problems in children with FASD: a Polish cohort"
author: "S. Roozen, K. Dylag, K. Przybyszewska, J. Niemczyk, A. von Gontard, G-J. Y. Peters, Kok, and L. Curfs"
date: "`r format(Sys.time(), '%d %b %Y at %H:%M:%S');`"
output:
  html_document: 
    toc: yes
    toc_float: true
    toc_depth: 5
---

Supplementary file on statistics



# HEADING

## Inspection of the data 

## Additional: correction for multiple testing



```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

require('userfriendlyscience');
safeRequire('ez');
safeRequire('pander');
safeRequire('plyr');
safeRequire('car');

panderOptions('table.split.table', Inf);


#getDat(filename="B:/Shared/Gjalt-Jorn & Sylvia/Incontinence/Incontinence Study FARR [24.06.2016]_6.sav");
getDat(filename="C:/Users/sylvia.roozen/Desktop/Sync/Data/Research/FASD/FASD Incontinence/analyses_incontinence_FASD_Polish_cohort_files/Incontinence Study Poland [SR 09.05.2018].sav",
                 applyRioLabels=FALSE);

```


# Inspection of the data

```{r}

### We'll have to do this manually.
categoricalVariables <- c('Living', 
                          'Q_completed', 
                          'School',
                          'School_mother',
                          'School_father',
                          'Medication', 
                          'AgeGroups',
                          'Sex', 
                          'FASD', 
                          'Code_Diagn',
                          'Incontinence_ALL',                    
                          'Incontinence_Overall',  
                          'NE_nocturnal_enuresis', 
                          'DUI_daytime_urinary_incontinence', 
                          'FI_fecal_incontinence',   
                          'Physical_disability_chronis_illness',  
                          'Q12', 'Q13', 'Q14');

intervalVariables <- c('Age_Years',
                       'IQ',
                       'OFC',
                       'HBD',
                       'AG',
                       'Birth_Weight',
                       'Height_cm',
                       'Weight_kg',
                       'computeBMI',
                       'BMIpercentiles', 
                       'LUTS_Score');

### Set categorical variabels to factors
dat[, categoricalVariables] <-
  lapply(dat[, categoricalVariables],
         function(x) {
           res <- factor(x,
                         levels=attr(x, 'labels'),
                         labels=names(attr(x, 'labels')));
         });

### number of unique values per variable
unlist(lapply(dat, function(x) return(length(unique(x)))));


### general sample characteristics


examine(dat$Living, dat$Physical_disability_chronis_illness, dat$Q_completed, dat$School,
        dat$School_mother, dat$School_father,
        dat$Medication, dat$AgeGroups,
        dat$Sex, dat$FASD, dat$Code_Diagn,
        stem = FALSE,
        extremeValues = FALSE);

examine(dat$Age_Years, dat$IQ,
        dat$HBD, dat$AG, dat$OFC,
        dat$Birth_Weight, dat$Height_cm,
        dat$Weight_kg, dat$computeBMI,
        dat$BMIpercentiles,
        dat$LUTS_Score,
        stem = FALSE,
        extremeValues = FALSE);



# dataShape(dat$Age_Years, dat$IQ, dat$OFC, dat$HBD, dat$AG, dat$Birth_Weight, dat$Height_cm, dat$Weight_kg, dat$computeBMI, dat$BMI_percentile, dat$LUTS_Score);

lapply(dat[, intervalVariables], dataShape);

### Assess normality of sampling distribution of the mean
lapply(dat[, intervalVariables], normalityAssessment);


### incontinence data

frequencies(dat$Incontinence_ALL, dat$Incontinence_Overall, dat$NE_nocturnal_enuresis, dat$DUI_daytime_urinary_incontinence, dat$FI_fecal_incontinence, dat$Q12, dat$Q13, dat$Q14,  plot=TRUE);




```

# 1. What is the prevalence of overall incontinence among individuals (aged 4-19yr) diagnosed within the FASD spectrum in Poland?
## 1.1-1.3 What is the prevalence of NE, DUI, FI among individuals (aged 4-19yr) diagnosed within the FASD spectrum in Poland?



```{r}
 
produceBinomTest <- function(vector, successValue) {
  if (sum(!is.na(vector)) < 1) {
    return(NULL);
  } else {
    return(binom.test(sum(vector == successValue, na.rm=TRUE),
                      sum(!is.na(vector)),
                      p=0));
  }
}

# ### Replace the 0 with continence in the general population to compare
prev_Incontinence_All <- produceBinomTest(dat$Incontinence_ALL, "All")
prev_Incontinence_Overall <- produceBinomTest(dat$Incontinence_Overall, 1);
prev_Incontinence_NE <- produceBinomTest(dat$NE_nocturnal_enuresis, 1);
prev_Incontinence_DUI <- produceBinomTest(dat$DUI_daytime_urinary_incontinence, "Yes");
prev_Incontinence_FI <- produceBinomTest(dat$FI_fecal_incontinence, "Yes");

# prev_Incontinence_All;
# prev_Incontinence_Overall;
# rev_Incontinence_NE;
# prev_Incontinence_DUI;
# prev_Incontinence_FI;

### per diagnosis

pander(ddply(dat, 'Code_Diagn', function(subdataframe) {
  df1 <- t(unlist(produceBinomTest(subdataframe$Incontinence_Overall, 1)[c('estimate', 'conf.int')]));
  df2 <- t(unlist(produceBinomTest(subdataframe$NE_nocturnal_enuresis, 1)[c('estimate', 'conf.int')]));
  df3 <- t(unlist(produceBinomTest(subdataframe$DUI_daytime_urinary_incontinence, "Yes")[c('estimate', 'conf.int')]));
  df4 <- t(unlist(produceBinomTest(subdataframe$FI_fecal_incontinence, "Yes")[c('estimate', 'conf.int')]));
  df5 <- t(unlist(produceBinomTest(subdataframe$Incontinence_ALL, "Yes")[c('estimate', 'conf.int')]));
  res <- data.frame(cbind(df1, df2, df3, df4, df5));
  names(res) <- c(paste0('Overall_', c('est', 'lo', 'hi')),
                  paste0('NE_', c('est', 'lo', 'hi')),
                  paste0('DUI_', c('est', 'lo', 'hi')),
                  paste0('FI_', c('est', 'lo', 'hi')),
                  paste0('ALL_', c('est', 'lo', 'hi')));
  return(res);
}));

### overall FASD 

  pander(ddply(dat, 'FASD', function(subdataframe) {
    df1 <- t(unlist(produceBinomTest(subdataframe$Incontinence_Overall, 1))[c('estimate', 'conf.int')]);
    df2 <- t(unlist(produceBinomTest(subdataframe$NE_nocturnal_enuresis, 1))[c('estimate', 'conf.int')]);
    df3 <- t(unlist(produceBinomTest(subdataframe$DUI_daytime_urinary_incontinence, "Yes"))[c('estimate', 'conf.int')]);
    df4 <- t(unlist(produceBinomTest(subdataframe$FI_fecal_incontinence, "Yes"))[c('estimate', 'conf.int')]);
    df5 <- t(unlist(produceBinomTest(subdataframe$Incontinence_ALL, 1))[c('estimate', 'conf.int')]);
    res <- data.frame(cbind(df1, df2, df3, df4, df5));
    names(res) <- c(paste0('Overall_', c('est', 'lo', 'hi')),
                    paste0('NE_', c('est', 'lo', 'hi')),
                    paste0('DUI_', c('est', 'lo', 'hi')),
                    paste0('FI_', c('est', 'lo', 'hi')),
                    paste0('ALL_', c('est', 'lo', 'hi')));
    return(res);
  }));


```

The confidence interval for the prevalence runs from `r  round(prev_Incontinence_Overall$conf.int[1], 2)` to `r  round(prev_Incontinence_Overall$conf.int[2], 2)`, and the point estimate for the prevalence is `r round(prev_Incontinence_Overall$estimate, 2)`.

The confidence interval for the prevalence NE runs from `r  round(prev_Incontinence_NE$conf.int[1], 2)` to `r  round(prev_Incontinence_NE$conf.int[2], 2)`, and the point estimate for the prevalence is `r round(prev_Incontinence_NE$estimate, 2)`.

The confidence interval for the prevalence NE runs from `r  round(prev_Incontinence_DUI$conf.int[1], 2)` to `r  round(prev_Incontinence_DUI$conf.int[2], 2)`, and the point estimate for the prevalence is `r round(prev_Incontinence_DUI$estimate, 2)`.

The confidence interval for the prevalence NE runs from `r  round(prev_Incontinence_FI$conf.int[1], 2)` to `r  round(prev_Incontinence_FI$conf.int[2], 2)`, and the point estimate for the prevalence is `r round(prev_Incontinence_FI$estimate, 2)`.

The confidence interval for the prevalence runs from `r  round(prev_Incontinence_All$conf.int[1], 2)` to `r  round(prev_Incontinence_All$conf.int[2], 2)`, and the point estimate for the prevalence is `r round(prev_Incontinence_All$estimate, 2)`.



# 2. What is the prevalence of overall incontinence_ALL (< once a month) among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?


```{r}

### Prevalence all Incontinence_All 

binom.test(sum(dat$Incontinence_ALL == 1), nrow(dat), p=0);
prev_Incontinence_ALL <- binom.test(sum(dat$Incontinence_ALL == 1), nrow(dat), p=0);

pander(prev_Incontinence_ALL);



```

# 3. What is the prevalence of specific symptoms among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?


```{r}

### Prevalence specific symptoms, questionnaire items Q12, Q13, Q14
## Error omdat hij de missing values niet leest?

binom.test(sum(dat$Q12[complete.cases(dat$Q12)] < 3), nrow(dat), p=0);
binom.test(sum(dat$Q13[complete.cases(dat$Q13)] < 3), nrow(dat), p=0);
binom.test(sum(dat$Q14[complete.cases(dat$Q14)] < 3), nrow(dat), p=0);


### Specific symptoms are not frequently present in children with FASD. Due to small 'n' it is not possible to calculate prevalence.

# dat$fasd_diagnosis <- factor(dat$FASD_diagn, levels=1:3, labels=names(rev(attr(dat$FASD_diagn, 'value.labels'))));
# 
# 
# ### To check
#   dat[, c('FASD_diagn', 'fasd_diagnosis')];
#   
#   pander(ddply(dat, 'fasd_diagnosis', function(subdataframe) {
#     df1 <- t(unlist(binom.test(sum(subdataframe$Straining == 1), nrow(subdataframe), p=0)[c('estimate', 'conf.int')]));
#     df2 <- t(unlist(binom.test(sum(subdataframe$Urgency == 1), nrow(subdataframe), p=0)[c('estimate', 'conf.int')]));
#     df3 <- t(unlist(binom.test(sum(subdataframe$Postponement == 1), nrow(subdataframe), p=0)[c('estimate', 'conf.int')]));
#     res <- data.frame(cbind(df1, df2, df3));
#     names(res) <- c(paste0('Straining', c('est', 'lo', 'hi')),
#                     paste0('Urgency', c('est', 'lo', 'hi')),
#                     paste0('Postponement', c('est', 'lo', 'hi')),
#     return(res);
#    }));


```


# 4. What is the mean average of LUTS among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean LUTS score
pander(meanConfInt(dat$LUTS_Score)$output);


```

# 5. What is the mean average of HBD among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean HBD score
pander(meanConfInt(dat$HBD[complete.cases(dat$HBD)])$output);


```

# 6. What is the mean average of Apgar scale among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean HBD score
pander(meanConfInt(dat$AG[complete.cases(dat$AG)])$output);


```
# 7. What is the mean average of BMI among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean BMI score
pander(meanConfInt(dat$BMI[complete.cases(dat$BMI)])$output);


```

# 8. What is the mean average of OFC among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean OFC score
pander(meanConfInt(dat$OFC[complete.cases(dat$OFC)])$output);


```

# 9. What is the mean average of height among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean Height score
pander(meanConfInt(dat$Height_cm[complete.cases(dat$Height_cm)])$output);

```

# 10. What is the mean average of weight among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean Weight score
pander(meanConfInt(dat$Weight_kg[complete.cases(dat$Weight_kg)])$output);


```

# 11. What is the mean average of birthweight among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean Birth_Weight score
pander(meanConfInt(dat$Birth_Weight[complete.cases(dat$Birth_Weight)])$output);


```

# 12. What is the mean average IQ among individuals (aged 4-19yr) diagnosed withing the FASD spectrum in Poland?

```{r}

### Mean IQ score
pander(meanConfInt(dat$IQ[complete.cases(dat$IQ)])$output);


```

# 13. Is there a sign. association between incontinence and gender?
# 14. Is there a sign. association between incontinence and FASD diagnosis?
# 15. Is there a sign. association between incontinence and medication use?
# 16. Is there a sign. association between incontinence and IQ groups (<70, >70)?
# 17. Is there a sign. association between incontinence and symptoms of Straining?
# 18. Is there a sign. association between incontinence and symptoms of Urgency?
# 19. Is there a sign. association between incontinence and symptoms of Postponement?
# 20. Is there a sign. association between incontinence and Age?
# 21. Is there a sign. association between incontinence and HBD?
# 22. Is there a sign. association between incontinence and OFC?
# 23. Is there a sign. association between incontinence and AG?
# 24. Is there a sign. association between incontinence and birthweight?
# 25. Is there a sign. association between incontinence and height?
# 26. Is there a sign. association between incontinence and weight?
# 27. Is there a sign. association between incontinence and IQ?
# 28. Is there a sign. association between incontinence and BMI?
# 29. Is there a sign. association between incontinence and BMI percentile?

```{r}

### Categorical associations 

crossTab(dat$Incontinence_Overall, factor(dat$Age_Groups_Three));
crossTab(dat$Incontinence_Overall, factor(dat$Age_Groups_Two));
crossTab(dat$Incontinence_Overall, dat$Age_Groups_Two_excl);
crossTab(dat$Incontinence_Overall, dat$Sex);
crossTab(dat$Incontinence_Overall, dat$FASD_diagn);
crossTab(dat$Incontinence_Overall, factor(dat$Medication));
crossTab(dat$Incontinence_Overall, factor(dat$IQ_Groups));
crossTab(dat$Incontinence_Overall, factor(dat$Q12));
crossTab(dat$Incontinence_Overall, factor(dat$Q13));
crossTab(dat$Incontinence_Overall, dat$Q14);


tmp <- lapply(categoricalVariables, function(currentVar) {
  cat("###", currentVar, "\n");
  print(fisher.test(dat$Incontinence_Overall, dat[, currentVar]));
});

# fisher.test(dat$Incontinence_Overall, factor(dat$Age_Groups_Three));
# fisher.test(dat$Incontinence_Overall, factor(dat$Age_Groups_Two));
# fisher.test(dat$Incontinence_Overall, dat$Age_Groups_Two_excl);
# fisher.test(dat$Incontinence_Overall, dat$Sex);
# fisher.test(dat$Incontinence_Overall, dat$FASD_diagn);
# fisher.test(dat$Incontinence_Overall, factor(dat$Medication));
# fisher.test(dat$Incontinence_Overall, factor(dat$IQ_Groups));
# fisher.test(dat$Incontinence_Overall, factor(dat$Q12));
# fisher.test(dat$Incontinence_Overall, factor(dat$Q13));
# fisher.test(dat$Incontinence_Overall, dat$Q14);

### Numerical associations 

meanDiff(dat$Age_Years ~ dat$Incontinence_Overall);
meanDiff(dat$HBD ~ dat$Incontinence_Overall);
meanDiff(dat$OFC ~ dat$Incontinence_Overall);
meanDiff(dat$AG ~ dat$Incontinence_Overall);
meanDiff(dat$Birth_Weight ~ dat$Incontinence_Overall);
meanDiff(dat$Height_cm ~ dat$Incontinence_Overall);
meanDiff(dat$Weight_kg ~ dat$Incontinence_Overall);
meanDiff(dat$IQ ~ dat$Incontinence_Overall);
meanDiff(dat$BMI ~ dat$Incontinence_Overall);
#meanDiff(dat$BMI_percentile ~ dat$Incontinence_Overall);


```

# 30. Is there a sign. association between FASD diagnose and gender?
# 31. Is there a sign. association between FASD diagnose and incontinence?
# 32. Is there a sign. association between FASD diagnose and medication use?
# 33. Is there a sign. association between FASD diagnose and IQ groups (<70, >70)?
# 34. Is there a sign. association between FASD diagnose and symptoms of Straining?
# 35. Is there a sign. association between FASD diagnose and symptoms of Urgency?
# 36. Is there a sign. association between FASD diagnose and symptoms of Postponement?
# 37. Is there a sign. association between FASD diagnose and Age?
# 38. Is there a sign. association between FASD diagnose and HBD?
# 39. Is there a sign. association between FASD diagnose and OFC?
# 40. Is there a sign. association between FASD diagnose and AG?
# 41. Is there a sign. association between FASD diagnose and birthweight?
# 42. Is there a sign. association between FASD diagnose and height?
# 43. Is there a sign. association between FASD diagnose and weight?
# 44. Is there a sign. association between FASD diagnose and IQ?
# 45. Is there a sign. association between FASD diagnose and BMI?
# 46. Is there a sign. association between FASD diagnose and BMI percentile?


```{r}

### Categorical associations 

crossTab(dat$Code_Diagn, dat$AgeGroups);
crossTab(dat$Code_Diagn, dat$Sex);
crossTab(dat$Code_Diagn, dat$Medication);
crossTab(dat$Code_Diagn, dat$Q21);
crossTab(dat$Code_Diagn, dat$Q13);
crossTab(dat$Code_Diagn, dat$Q14);
crossTab(dat$Code_Diagn, dat$Incontinence_Overall);

tmp <- lapply(categoricalVariables, function(currentVar) {
  cat("###", currentVar, "\n");
  print(fisher.test(dat$Code_Diagn, dat[, currentVar]));
});


### Numerical associations 

#oneway(dat$Age_Years, dat$FASD_diagn, means=TRUE, levene=TRUE, corrections=TRUE, plot=TRUE);

oneway(dat$Age_Years, dat$Code_Diagn);
oneway(dat$HBD, dat$Code_Diagn);
oneway(dat$OFC, dat$Code_Diagn);
oneway(dat$AG, dat$Code_Diagn);
oneway(dat$Birth_Weight, dat$Code_Diagn);
oneway(dat$Height_cm, dat$Code_Diagn);
oneway(dat$Weight_kg, dat$Code_Diagn);
oneway(dat$IQ, dat$Code_Diagn);
oneway(dat$computeBMI, dat$Code_Diagn);
#oneway(dat$BMI_percentile, dat$Code_Diagn);


```


# 47. Is there a sign. association between gender and FASD diagnose?
# 48. Is there a sign. association between gender and incontinence?
# 49. Is there a sign. association between gender and medication use?
# 50. Is there a sign. association between gender and IQ groups (<70, >70)?
# 51. Is there a sign. association between gender and symptoms of Straining?
# 52. Is there a sign. association between gender and symptoms of Urgency?
# 53. Is there a sign. association between gender and symptoms of Postponement?
# 54. Is there a sign. association between gender and Age?
# 55. Is there a sign. association between gender and HBD?
# 56. Is there a sign. association between gender and OFC?
# 57. Is there a sign. association between gender and AG?
# 58. Is there a sign. association between gender and birthweight?
# 59. Is there a sign. association between gender and height?
# 60. Is there a sign. association between gender and weight?
# 61. Is there a sign. association between gender and IQ?
# 62. Is there a sign. association between gender and BMI?
# 63. Is there a sign. association between gender and BMI percentile?


```{r}

### Categorical associations 

#crossTab(dat$Sex, dat$AgeGroups);
#crossTab(dat$Sex, dat$FASD);
#crossTab(dat$Sex, dat$Medication);
#crossTab(dat$Sex, dat$Q12);
#crossTab(dat$Sex, dat$Q13);
#crossTab(dat$Sex, dat$Q14);
#crossTab(dat$Sex, dat$Incontinence_Overall);

#tmp <- lapply(categoricalVariables, function(currentVar) {
#  cat("###", currentVar, "\n");
#  print(fisher.test(dat$Sex, dat[, currentVar]));
#});


### Numerical associations 

#meanDiff(dat$Age_Years ~ dat$Sex);
#meanDiff(dat$HBD ~ dat$Sex);
#meanDiff(dat$OFC ~ dat$Sex);
#meanDiff(dat$AG ~ dat$Sex);
#meanDiff(dat$Birth_Weight ~ dat$Sex);
#meanDiff(dat$Height_cm ~ dat$Sex);
#meanDiff(dat$Weight_kg ~ dat$Sex);
#meanDiff(dat$IQ ~ dat$Sex);
#meanDiff(dat$BMI ~ dat$Sex);
#meanDiff(dat$BMI_percentile ~ dat$Sex);


```

# 64. Is there a sign. association between age and FASD diagnose?
# 65. Is there a sign. association between age and incontinence?
# 66. Is there a sign. association between age and medication use?
# 67. Is there a sign. association between age and IQ groups (<70, >70)?
# 68. Is there a sign. association between age and symptoms of Straining?
# 69. Is there a sign. association between age and symptoms of Urgency?
# 70. Is there a sign. association between age and symptoms of Postponement?
# 71. Is there a sign. association between age and gender?
# 72. Is there a sign. association between age and HBD?
# 73. Is there a sign. association between age and OFC?
# 74. Is there a sign. association between age and AG?
# 75. Is there a sign. association between age and birthweight?
# 76. Is there a sign. association between age and height?
# 77. Is there a sign. association between age and weight?
# 78. Is there a sign. association between age and IQ?
# 79. Is there a sign. association between age and BMI?
# 80. Is there a sign. association between age and BMI percentile?

```{r}

### Age als continues variable with continues variables

scatterPlot(dat$HBD, dat$Age_Years);
cor.test(dat$HBD, dat$Age_Years);

scatterPlot(dat$OFC, dat$Age_Years);
cor.test(dat$OFC, dat$Age_Years);

scatterplot(dat$AG, dat$Age_Years);
cor.test(dat$AG, dat$Age_Years);

scatterplot(dat$Birth_Weight, dat$Age_Years);
cor.test(dat$Birth_Weight, dat$Age_Years);

scatterplot(dat$Height_cm, dat$Age_Years);
cor.test(dat$Height_cm, dat$Age_Years);

scatterplot(dat$Weight_kg, dat$Age_Years);
cor.test(dat$Weight_kg, dat$Age_Years);

scatterplot(dat$IQ, dat$Age_Years);
cor.test(dat$IQ, dat$Age_Years);

scatterplot(dat$BMI, dat$Age_Years);
cor.test(dat$BMI, dat$Age_Years);

#scatterplot(dat$BMI_percentile, dat$Age_Years);
#cor.test(dat$BMI_percentile, dat$Age_Years);


### Age als continues variable with categorical (ordinal) variables.

oneway(dat$Age_Years, dat$Sex, plot=TRUE);
oneway(dat$Age_Years, dat$Medication, plot=TRUE);
oneway(dat$Age_Years, dat$Code_Diagn, plot=TRUE);
#oneway(dat$Age_Years, dat$Q12, plot=TRUE);
oneway(dat$Age_Years, dat$Q13, plot=TRUE);
oneway(dat$Age_Years, dat$Q14, plot=TRUE);


# plot(dat$Sex ~ dat$Age_Years);
# aov(dat$Medication ~ dat$Age_Years);
# plot(dat$Medication ~ dat$Age_Years);
# aov(dat$FASD_diagn ~ dat$Age_Years);
# plot(dat$FASD_diagn ~ dat$Age_Years);
# aov(dat$IQ_Groups ~ dat$Age_Years);
# plot(dat$IQ_Groups ~ dat$Age_Years);
# aov(dat$Straining ~ dat$Age_Years);
# plot(dat$Straining ~ dat$Age_Years);
# aov(dat$Urgency ~ dat$Age_Years);
# plot(dat$Urgency ~ dat$Age_Years);
# aov(dat$Postponement ~ dat$Age_Years);
# plot(dat$Postponement ~ dat$Age_Years);

```

# Additional: correction for multiple testing

```{r}

## Correction for multiple testing

pValues <- data.frame(p = c(.748,
                            .986,
                            .76,
                            .325,
                            .729,
                            .072,
                            .508,
                            .66,
                            .393,
                            .199,
                            .175,
                            .883,
                            .332,
                            .162,
                            .549,
                            .153,
                            .053,
                            .618,
                            .022,
                            .028,
                            .032,
                            .007,
                            .029,
                            .248,
                            .725,
                            .951,
                            .256,
                            .249,
                            .381,
                            .729,
                            .026,
                            .477,
                            .175,
                            .409,
                            .138,
                            .029,
                            .098,
                            .722,
                            .613,
                            .194,
                            .354,
                            .754,
                            .791,
                            .248,
                            .83,
                            .692,
                            .139,
                            .22,
                            .305,
                            .325,
                            .999,
                            .535,
                            .919,
                            .304,
                            .469,
                            .899,
                            .502,
                            .281,
                            .281,
                            .487,
                            .931,
                            .000000001,
                            .975,
                            .304,
                            .000000001,
                            .000000001,
                            .095,
                            .000000001,
                            .235,
                            .999,
                            .01,
                            .026,
                            .193,
                            .388,
                            .579));
pValues$names <- c("association between Incontinence overall and Age Groups in 3 groups (children, adolescents, adults)",
                   "association between Incontinence overall and Age Groups in 2 groups (children, adolescent incl adults)",
                   "association between Incontinence overall and Age Groups in 2 groups (children and adolescents)",
                   "association between Incontinence overall and Gender",
                   "association between Incontinence overall and FASD diagnosis",
                   "association between Incontinence overall and use of medication",
                   "association between Incontinence overall and IQ groups <70 and >70",
                   "association between Incontinence overall and Straining",
                   "association between Incontinence overall and Postponement",
                   "association between Incontinence overall and Urgency",
                   "association between Incontinence overall and Age in years (continues variable)",
                   "association between Incontinence overall and HBD",
                   "association between Incontinence overall and OFC",
                   "association between Incontinence overall and Apgar scale score",
                   "association between Incontinence overall and Birth weight",
                   "association between Incontinence overall and Height in cm",
                   "association between Incontinence overall and Weight in kg",
                   "association between Incontinence overall and IQ",
                   "association between Incontinence overall and BMI",
                   "association between Incontinence overall and BMI percentile",
                   "association between FASD diagnosis and Age Groups in 3 groups (children, adolescents, adults)",
                   "association between FASD diagnosis and Age Groups in 2 groups (children, adolescents incl adults)",
                   "association between FASD diagnosis and Age Groups in 2 groups (children and adolescents)",
                   "association between FASD diagnosis and Gender",
                   "association between FASD diagnosis and use of medication",
                   "association between FASD diagnosis and IQ groups <70 and >70",
                   "association between FASD diagnosis and Straining",
                   "association between FASD diagnosis and Postponement",
                   "association between FASD diagnosis and Urgency",
                   "association between FASD diagnosis and Incontinence overall",
                   "association between FASD diagnosis and Age in years (continues variable)",
                   "association between FASD diagnosis and HBD",
                   "association between FASD diagnosis and OFC",
                   "association between FASD diagnosis and Apgar scale score",
                   "association between FASD diagnosis and Birth weight",
                   "association between FASD diagnosis and Height in cm",
                   "association between FASD diagnosis and Weight in kg",
                   "association between FASD diagnosis and IQ",
                   "association between FASD diagnosis and BMI",
                   "association between FASD diagnosis and BMI percentile",
                   "association between Gender and Age Groups in 3 groups (children, adolescents, adults)",
                   "association between Gender and Age Groups in 2 groups (children, adolescent incl adults)",
                   "association between Gender and Age Groups in 2 groups (children and adolescents)",
                   "association between Gender and FASD diagnosis",
                   "association between Gender and use of medication",
                   "association between Gender and IQ groups <70 and >70",
                   "association between Gender and Straining",
                   "association between Gender and Postponement",
                   "association between Gender and Urgency",
                   "association between Gender and Incontinence overall",
                   "association between Gender and Age in years (continues variable)",
                   "association between Gender and HBD",
                   "association between Gender and OFC",
                   "association between Gender and Apgar scale score",
                   "association between Gender and Birth weight",
                   "association between Gender and Height in cm",
                   "association between Gender and Weight in kg",
                   "association between Gender and IQ",
                   "association between Gender and BMI",
                   "association between Gender and BMI percentile",
                   "correlation between Age and HBD",
                   "correlation between Age and OFC",
                   "correlation between Age and Apgar scale score",
                   "correlation between Age and Birth weight",
                   "correlation between Age and Height in cm",
                   "correlation between Age and Weight in kg",
                   "correlation between Age and IQ",
                   "correlation between Age and BMI",
                   "correlation between Age and BMI percentile",
                   "correlation between Age and gender",
                   "correlation between Age and use of medication",
                   "correlation between Age and FASD diagnosis",
                   "correlation between Age and IQ groups <70 and >70",
                   "correlation between Age and Urgency",
                   "correlation between Age and Postponement");

pValues$bonferroni <- p.adjust(pValues$p, method='bonferroni');
pValues$holm <- p.adjust(pValues$p, method='holm');
pValues$fdr <- p.adjust(pValues$p, method='fdr');

pander(pValues[, c(2, 1, 3:ncol(pValues))]);



```




```{r}

### Toevoegingen op basis van overleg dinsdag 2016-10-25

### Convert all categorical variables into factors
#categoricalVariables <- c('Sex');

### Recode into categories,
### convert into factor with labels,
### and verify by comparing to original variable
#dat$AgeGroups <- recode(dat$Age,
#                        'lo:13=1 ; 13:18=2 ; 18:hi=3 ; else=NA');
#dat$AgeGroups <- factor(dat$AgeGroups, levels=c(1,2,3),
#                        labels=c('<13', '13-18', '>18'));
#pander(table(dat$Age, dat$AgeGroups));



#dat[, categoricalVariables] <- lapply(dat[, categoricalVariables, drop=FALSE], factor);

# variablesForAssociationMatrix <- 
#   c('Sex', 'Age', 'LUTS_Score', 'BMI', 'FASD_diagn', 'Straining', 'Postponement', 'Urgency', 'IQ_Groups', 'Incontinence_Overall';
# 
# pander(associationMatrix(dat[, variablesForAssociationMatrix], colNames=TRUE)$output$matrix$full);

```
